\documentclass{article}

\title{ECO210H1 Mathematical Methods for Economic Theory: Notes}
\author{Tianyu Du}
\date{\today}

\usepackage{spikey}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{soul}
\usepackage{float}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{chngcntr}

\counterwithin*{equation}{section}

\begin{document}
	\maketitle
	\tableofcontents
	
	\section{Quadratic Forms}
		\begin{definition}[Quadratic Form]
			\[
				Q(\textbf{x}) = \textbf{x}' \textbf{A} \textbf{x}
			\]
			where $\textbf{x} \in \R^n$ and \hl{symmetric} $\textbf{A} \in \mathbb{M}_{n\times n}$.
		\end{definition}
		
		\begin{definition}[Definiteness of Quadratic Form]
			Let $\mc{Q}$ be a quadratic form
			\begin{enumerate}
				\item Positive definite.
				\item Negative definite
				\item Positive semidefinite.
				\item Negative semidefinite.
				\item Indefinite.
			\end{enumerate}
		\end{definition}
		
		\begin{definition}[$k^{th}$ Order Leading Principal Minor]
			
		\end{definition}
		
		\begin{proposition}
			Let \textbf{A} be an $n\times n$ \hl{symmetric} matrix, and let $D_k$ where $k = 1,\dots, n$ be its leading principal minors. Then
			\begin{enumerate}
				\item \textbf{A} is positive definite $\iff$ $D_k > 0\ \forall k$. 
				\item \textbf{A} is negative definite $\iff$ $(-1)^k D_k > 0\ \forall k$.
			\end{enumerate}
		\end{proposition}
		
		\begin{definition}[$k^{th}$ Order Principal Minor]
			
		\end{definition}
		
		\begin{proposition}
			Let \textbf{A} be a $n \times n$ \hl{symmetric} matrix. Then
			\begin{enumerate}
				\item \textbf{A} is positive semidefinite $\iff$ all its principal minors are non-negative.
				\item \textbf{A} is negative semidefinite $\iff$ all its $k^{th}$ order principal minors are non-positive for $k$ odd and non-negative for $k$ even.
			\end{enumerate}
		\end{proposition}
	
	\section{Concavity and Convexity}
		\begin{definition}[Convex Sets in $\R^n$]
			A set $S \subseteq \R^n$ is convex if for all $\textbf{x}^1 \in S$ and $\textbf{x}^2 \in S$, we have
			\[
				t \textbf{x}^1 + (1-t)\textbf{x}^2 \in S
			\]
			for all $t \in [0, 1]$.
		\end{definition}
		
		\begin{definition}[Convex Combination]
			Given a finite number of points $\vec{x}_1, \vec{x}_2, \dots \vec{x}_n$ in a real vector space, a convex combination of these points is
			\[
				\vec{x} = \sum_{i=1}^n \alpha_i \vec{x}_i
			\]
			where 
			\[
				\sum_{i=1}^n \alpha_i = 1 \land a_i \geq 0\ \forall i
			\]
		\end{definition}
		
		\begin{definition}[Convex Hull (of a finite point set)]
			Let $S$ be a finite set of vectors from a real vector space,
			\[
				Conv(S) = \Big \{
					\sum_{i=1}^{|S|} \alpha_i x_i \Big | (\alpha_i \geq 0\ \forall i) \land \sum_{i=1}^{|S|} \alpha_i = 1
				\Big \}
			\]
		\end{definition}
		
		\begin{definition}[Affine Combination]
			\[
				\vec{x} = \sum_{i=1}^n \alpha_i \vec{x}_i
			\]
			where 
			\[
				\sum_{i=1}^n \alpha_i = 1
			\]
		\end{definition}
		
		\begin{proposition}
			The intersection of convex sets is convex.
		\end{proposition}
		
		\begin{definition}[Concave Function]
			Let $D \subseteq \R^n$ be convex and $f: D\to \R$ is \textbf{concave} if for all $\textbf{x}_1, \textbf{x}_2 \in D$
			\[
				f(t \textbf{x}_1 + (1-t) \textbf{x}_2) \geq t f(\textbf{x}_1) + (1-t) f(\textbf{x}_2)\quad \forall t \in [0, 1]
			\]
		\end{definition}
		
		\begin{definition}[Convex Function]
			Let $D \subseteq \R^n$ be convex and $f: D\to \R$ is \textbf{convex} if for all $\textbf{x}_1, \textbf{x}_2 \in D$
			\[
				f(t \textbf{x}_1 + (1-t) \textbf{x}_2) \leq t f(\textbf{x}_1) + (1-t) f(\textbf{x}_2)\quad \forall t \in [0, 1]
			\]
		\end{definition}
		
		\begin{definition}[Strictly Concave Function]
			$f: D \to \R$ is \textbf{strictly concave} if and only if, for all $\textbf{x}_1 \neq \textbf{x}_2 \in D$,
			\[
				f(t \textbf{x}_1 + (1-t) \textbf{x}_2) > t f(\textbf{x}_1) + (1-t) f(\textbf{x}_2)\quad \forall t \in (0, 1)
			\]
		\end{definition}
		
		\begin{theorem}
			$f: D \to \R$ defined on a convex set is 
			\begin{enumerate}
				\item Concave if and only if set 
				\[
					A \equiv \{(\textbf{x}, y): \textbf{x} \in S, y \leq f(\textbf{x})\}
				\]
				is convex. 
				\item Convex if and only if set 
				\[
					A \equiv \{(\textbf{x}, y): \textbf{x} \in S, y \geq f(\textbf{x})\}
				\]
				is convex.
			\end{enumerate}
		\end{theorem}
		
		\begin{theorem}[Jensen's Inequality]
			Let $f: D \to \R$ defined on a convex set is concave if and only if for all $n \geq 2$,
			\[
				f(\sum_{i=1}^n \lambda_i \textbf{x}_i) \geq \sum_{i=1}^n \lambda_i f(\textbf{x}_i)
			\]
			where 
			\[
				(\forall i: \lambda_i \geq 0) \land \sum_{i=1}^n \lambda_i = 1
			\]
			and $f$ is convex if and only if for all $n \geq 2$,
			\[
				f(\sum_{i=1}^n \lambda_i \textbf{x}_i) \leq \sum_{i=1}^n \lambda_i f(\textbf{x}_i)
			\]
			where 
			\[
				(\forall i: \lambda_i \geq 0) \land \sum_{i=1}^n \lambda_i = 1
			\]
		\end{theorem}
		
	\section{Optimization: definitions}
\end{document}



























